\documentclass{article}
\usepackage{amsmath}
\usepackage{xcolor}

\begin{document}

\textbf{Student Answer:}
\begin{align*}
1: & \quad (2y+6)\frac{dy}{dx}=4-2x \\
2: & \quad \frac{dy}{dx}=\frac{4-2x}{2y+6} \\
3: & \quad +at(11,0)=\frac{1}{3} \\
4: & \quad y=\frac{1}{3x}-\frac{11}{3} \\
5: & \quad 0 +a+(-70)=-3 \\
6: & \quad y=-3x-21 \\
7: & \quad \frac{1}{3}x=\frac{11}{3}=-3x-21 \\
8: & \quad \frac{10}{3}x=-\frac{52}{3} \\
9: & \quad x=-3.2 \quad y=-3.4 \\
\end{align*}

\textbf{Feedback and Grade:}
\begin{itemize}
\item[Mark 1] \textcolor{red}{The student did not write the center of the circle as (2,-3).}
\item[Mark 2] \textcolor{red}{The student did not show a correct method for finding the gradient of the line AC.}
\item[Mark 3] \textcolor{green}{The student found the gradient of the tangent at A as 3 in step 3.}
\item[Mark 4] \textcolor{green}{The student found the equation of the tangent at A as $y=-3x-21$ in step 6.}
\item[Mark 5] \textcolor{red}{The student did not show a correct method for finding the point of intersection of the tangent lines.}
\item[Mark 6] \textcolor{red}{The student did not find the correct coordinates of the point of intersection of the tangent lines.}
\end{itemize}

\textbf{Score: 2/6}

\textbf{Comments:} You have found the gradient of the tangent at A and the equation of the tangent at A correctly. However, you did not find the center of the circle, the gradient of the line AC, or the correct method for finding the point of intersection of the tangent lines. Please review the concepts of circle equations, gradients, and tangent lines to improve your understanding. Keep practicing!

\end{document}