\documentclass{article}
\usepackage{amsmath}
\usepackage{xcolor}

\begin{document}

\textbf{Student Answer:}
\begin{align*}
Step 1: & (x^{2}-4x+4)-4+(y^{2}+6y+9)-9-77=0 \\
Step 2: & (x-2)^{2}+(y+3)^{2}=9 \\
Step 3: & (2,-3) \\
Step 4: & h=(11-2)/(h-3)=3 \\
Step 5: & k!=-(1)/(3) \\
Step 6: & (y-0)=-(1)/(3)(x-11) \\
Step 7: & y=-(1)/(3)x+(11)/(3) \\
Step 8: & h_2=(2+7)/(-3+2)=-3 \\
Step 9: & k _|_ k=(1)/(3) \\
Step 10: & (y-0)=(1)/(3)(x+7) \\
Step 11: & y=(1)/(3)x+(7)/(3) \\
Step 12: & (1)/(3)x+(7)/(3)=-(1)/(3)x+(11)/(3) \\
Step 13: & (2)/(3)x=(4)/(3) \\
Step 14: & x=2 \\
\end{align*}

\textbf{Feedback and Grade:}
\begin{itemize}
\item[Mark 1] \textcolor{green}{You correctly identified the center of the circle as (2,-3) in step 3. Well done!}
\item[Mark 2] \textcolor{red}{You did not show a correct method for finding the gradient of the line AC. This step is missing in your solution.}
\item[Mark 3] \textcolor{red}{You did not correctly find the gradient of the tangent at A or B. The gradients you found in steps 4 and 8 are not correct.}
\item[Mark 4] \textcolor{red}{The equations of the tangents you found in steps 6 and 10 are not correct.}
\item[Mark 5] \textcolor{red}{You did not correctly find the point of intersection of the tangent lines. The equation you found in step 12 is not correct.}
\item[Mark 6] \textcolor{red}{The coordinates of the point of intersection you found in step 14 are not correct.}
\end{itemize}

\textbf{Score: 1/6}

\textbf{Comments:} You have a good start by correctly identifying the center of the circle. However, you seem to struggle with finding the gradients of the tangent lines and the point of intersection of these lines. I recommend reviewing the method for finding the gradient of a line and how to find the point of intersection of two lines. Keep practicing and don't hesitate to ask for help if you need it!

\end{document}