\documentclass{article}
\usepackage{amsmath}
\usepackage{xcolor}

\begin{document}

\textbf{Student Answer:}
\begin{align*}
Step 1: & (x^{2}-4x+4)-4+(y^{2}+6y+9)-9-77=0 \\
Step 2: & (x-2)^{2}+(y+3)^{2}=9 \\
Step 3: & (2,-3) \\
Step 4: & h=(11-2)/(0-3))=3 \\
Step 5: & k!=-(1)/(3) \\
Step 6: & (y-0)=-(1)/(3)(x-11) \\
Step 7: & y=-(1)/(3)x+(11)/(3) \\
Step 8: & h_2=(2+7)/(-3-2)=-3 \\
Step 9: & k _|_ k=(1)/(3) \\
Step 10: & (y-0)=(1)/(3)(x+7) \\
Step 11: & y=(1)/(3)x+(7)/(3) \\
Step 12: & (1)/(3)x+(7)/(3)=-(1)/(3)x+(11)/(3) \\
Step 13: & (2)/(3)x=(4)/(3) \\
Step 14: & x=2 \\
\end{align*}

\textbf{Feedback and Grade:}
\begin{itemize}
\item[Mark 1] \textcolor{green}{You correctly identified the center of the circle as (2,-3) in step 3. Well done!}
\item[Mark 2] \textcolor{red}{You did not show a correct method for finding the gradient of the line AC. Remember, the gradient is the change in y divided by the change in x.}
\item[Mark 3] \textcolor{green}{You correctly found the gradients of the tangents at A and B in steps 4 and 8. Good job!}
\item[Mark 4] \textcolor{red}{You did not correctly find the equations of the tangents. Be careful with your algebra in steps 6 and 10.}
\item[Mark 5] \textcolor{red}{You did not correctly find the x-coordinate of the point of intersection. Check your algebra in step 13.}
\item[Mark 6] \textcolor{red}{You did not find the coordinates of the point of intersection of the tangent lines. This is a crucial step in the problem.}
\end{itemize}

\textbf{Score: 2/6}

\textbf{Comments:} You've made a good start by correctly identifying the center of the circle and the gradients of the tangents. However, you need to work on your algebra skills, particularly when finding the equations of the tangents and the point of intersection. Keep practicing and don't get discouraged!

\end{document}