\documentclass{article}
\usepackage{amsmath}
\usepackage{xcolor}

\begin{document}

\textbf{Student Answer:}
\begin{align*}
Step 1: & (x^{2}-4x+4)-4+(y^{2}+6y+9)-9-77=0 \\
Step 2: & (x-2)^{2}+(y+3)^{2}=9 \\
Step 3: & (2,-3) \\
Step 4: & h=(11-2)/(h-3)=3 \\
Step 5: & k\neq-(1)/(3) \\
Step 6: & (y-0)=-(1)/(3)(x-11) \\
Step 7: & y=-(1)/(3)x+(11)/(3) \\
Step 8: & h_2=(2+7)/(-3+2)=-3 \\
Step 9: & k \perp k=(1)/(3) \\
Step 10: & (y-0)=(1)/(3)(x+7) \\
Step 11: & y=(1)/(3)x+(7)/(3) \\
Step 12: & (1)/(3)x+(7)/(3)=-(1)/(3)x+(11)/(3) \\
Step 13: & (2)/(3)x=(4)/(3) \\
Step 14: & x=2 \\
\end{align*}

\textbf{Feedback and Grade:}
\begin{itemize}
\item[Mark 1] \textcolor{green}{You correctly identified the center of the circle as (2,-3) in Step 3. Well done!}
\item[Mark 2] \textcolor{red}{You did not show a correct method for finding the gradient of the line AC. This mark is lost.}
\item[Mark 3] \textcolor{green}{You correctly found the gradients of the tangents at A and B in Steps 4 and 8. Good job!}
\item[Mark 4] \textcolor{green}{You correctly wrote the equations of the tangents in Steps 6 and 10. Excellent work!}
\item[Mark 5] \textcolor{green}{You correctly found the x-coordinate of the point of intersection in Step 14. Well done!}
\item[Mark 6] \textcolor{red}{You did not find the coordinates of the point of intersection of the tangent lines. This mark is lost.}
\end{itemize}

\textbf{Score: 4/6}

\textbf{Comments:} You've done a good job overall, but there are a couple of areas where you could improve. Make sure to show your method for finding the gradient of the line AC. Also, don't forget to find the y-coordinate of the point of intersection of the tangent lines. Keep practicing and you'll get there!

\end{document}